\pkg{openTSNE}: A Modular \proglang{Python} Library for t-SNE Dimensionality Reduction and Embedding

### 2023-08-24 2023-08-final-revision/main.tex
paper: keywords should be lower-case

%% - \Keywords{} with LaTeX markup, at least one required
%% - \Plainkeywords{} without LaTeX markup (if necessary)
%% - Should be comma-separated and in sentence case.
\Keywords{t-SNE, Embedding, Visualization, Dimensionality reduction, \proglang{Python}}
\Plainkeywords{t-SNE, Embedding, Visualization, Dimensionality reduction, Python}

>>>>

%% - \Keywords{} with LaTeX markup, at least one required
%% - \Plainkeywords{} without LaTeX markup (if necessary)
%% - Should be comma-separated and in sentence case.
\Keywords{t-SNE, embedding, visualization, dimensionality reduction, \proglang{Python}}
\Plainkeywords{t-SNE, embedding, visualization, dimensionality reduction, Python}
